\bf\mftitle

### 2011-03-01 doc/jInfer/projecttype/projecttype.tex
3187368 - Review documentation: cleanup - projecttype mangling after rio

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer: & Michal Švirec \\ \hline
Required tokens:       & cz.cuni.mff.ksi.jinfer.base.interfaces.inference.IGGenerator \\
 & cz.cuni.mff.ksi.jinfer.base.interfaces.inference.SchemaGenerator \\
 & cz.cuni.mff.ksi.jinfer.base.interfaces.inference.Simplifier \\
 & org.openide.windows.IOProvider \\ \hline
Provided tokens:       & none \\ \hline
Module dependencies:   & Base \\
	& Runner \\ \hline
Public packages:       & cz.cuni.mff.ksi.jinfer.projecttype.actions \\ \hline
\end{tabular}

@@

\code{JinferProject} class implements the \code{Project} interface from NBP and represents an in-memory representation of a jInfer project. Inner structure of this class is very simple, interface specifies only two methods: \code{getProjectDirectory()} and \code{getLookup()}. All the extensibility of a project type is done by the \emph{Lookup} functionality of NBP. Project lookup contains properties, \code{Input} class (encapsulating input files), class creating output files, class building project tree in the Projects view, etc.

@@

A category in the properties window is represented by NBP \code{ProjectCustomizer.Category} class, properties pane is represented by \code{JPanel} class. Classes responsible for creation of this properties window are \code{JInferCustomizerProvider} and \code{JInferComponentProvider}. From jInfer module point of view the properties category is represented by \code{Properties\-Panel\-Provider} interface and associated properties pane by \code{AbstractPropertiesPanel} abstract class. How to use this interface and abstract class to create custom project properties category presented in jInfer project properties window is described in section \ref{properties_reg}.\\

\code{JInferComponentProvider} is a very simple class that extends \code{ProjectCustomizer.CategoryComponentProvider} class from NBP and its only method is \code{create()} which takes category as a parameter and returns properties pane. In the \code{JInferCustomizer\-Provider} class (which extends NBP \code{CustomizerProvider} class) is the core functionality of collecting categories (\code{PropertiesPanelProvider} interface) with associated properties panes (\code{AbstractPropertiesPanel} class) from all jInfer modules.\\

@@

As was written before, each jInfer project properties category is represented in jInfer modules by \code{PropertiesPanelProvider} interface. To create new category, this interface must be implemented and implementation must be annotated by the following code.
\begin{verbatim}
	@ServiceProvider(service = PropertiesPanelProvider.class)
\end{verbatim}

>>>>

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer & Michal Švirec \\ \hline
Required tokens       & \code{cz.cuni.mff.ksi.jinfer.base.interfaces.inference.IGGenerator} \\
 & \code{cz.cuni.mff.ksi.jinfer.base.interfaces.inference.SchemaGenerator} \\
 & \code{cz.cuni.mff.ksi.jinfer.base.interfaces.inference.Simplifier} \\
 & \code{org.openide.windows.IOProvider} \\ \hline
Provided tokens       & none \\ \hline
Module dependencies   & Base \\
	& Runner \\ \hline
Public packages       & \code{cz.cuni.mff.ksi.jinfer.projecttype.actions} \\ \hline
\end{tabular}

@@

\code{JinferProject} class implements the \code{Project} interface from NBP and represents an in-memory representation of a jInfer project. Inner structure of this class is very simple, interface specifies only two methods: \code{getProject\.Directo\.ry()} and \code{getLookup()}. All the extensibility of a project type is done by the \emph{Lookup} functionality of NBP. Project lookup contains properties, \code{Input} class (encapsulating input files), class creating output files, class building project tree in the Projects view, etc.

@@

A category in the properties window is represented by NBP \code{Project\.Customizer.\.Category} class, properties pane is represented by \code{JPanel} class. Classes responsible for creation of this properties window are \code{JInfer\.Customizer\.Provider} and \code{JInfer\.Component\.Provider}. From jInfer module point of view the properties category is represented by \code{Properties\.Panel\.Provider} interface and associated properties pane by \code{Abstract\.Properties\.Panel} abstract class. How to use this interface and abstract class to create custom project properties category presented in jInfer project properties window is described in section \ref{properties_reg}.\\

\code{JInferComponentProvider} is a very simple class that extends \code{ProjectCustomizer.Category\.Component\.Provider} class from NBP and its only method is \code{create()} which takes category as a parameter and returns properties pane. In the \code{JInfer\.Customizer\.Provider} class (which extends NBP \code{Customizer\.Provider} class) is the core functionality of collecting categories (\code{Properties\.Panel\.Provider} interface) with associated properties panes (\code{Abstract\.Properties\.Panel} class) from all jInfer modules.\\

@@

As was written before, each jInfer project properties category is represented in jInfer modules by \code{Properties\.Panel\.Provider} interface. To create new category, this interface must be implemented and implementation must be annotated by the following code.
\begin{verbatim}
	@ServiceProvider(service = PropertiesPanelProvider.class)
\end{verbatim}
